\documentclass[12pt]{report}
\usepackage{graphicx}
\usepackage{indentfirst}
\begin{document}
\title{Virus Versus the immune System}
\author{Sean Connolly\\
The Evergreen State College\\
Methods of Applied Mathematics\\
professorpi@hotmail.com}
\date{\today}
\maketitle

\section*{Introduction}

\section*{Viruses}

\section*{White Blood Cells}

\section*{Host cells}

\section*{Conclusion}

\begin{thebibliography} {9}
	\bibitem{Levy}
	  Steven Levy,
	  \emph{Blood}
	  Viking Penguin, New York,
	  1984.
	\bibitem{Menezes}
	  Alfred J. Menezes, Paul C van Oorshot, and Scott A. Vanstone,
	  \emph{Handbook of Applied Cryptography}
	  CRC Press, New York,
	  1997.
	\bibitem{Mel}
	  Cary Meltzer and Doris Baker,
	  \emph{Cryptography Decrypted}
	  Addison-Wesley, New York,
	  Second Printing
	  2001.
	\bibitem{Simmons}
	  Gustavus J. Simmons,
	  \emph{Contemporary Cryptology, The Science of Information Integrity}
	  IEEE Press, New York,
	  1992.
	\bibitem{ceaser}
	  The Institute for Math and Science Education of the University of Illinois at Chicago,
	  \emph{Cryptography, The Mathematics of Secret Codes}
	  http://cryptoclub.math.uic.edu/about/aboutbook.htm,
	  2004.
	\bibitem{DES}
	  Greg Sterijevski,
	  \emph{The Data E,cryption Standard}
	  http://raphael.math.uic.edu/~jeremy/crypt/contrib/stj.html,
	  Retrieved 2005.
	\bibitem{algorithm}
	  Arnoud Engelfriet,
	  \emph{The DES encryption algorithm}
	  http://www.iusmentis.com/technology/encryption/des/,
	  2003.
	\bibitem{DESalgorithm}
	  Arnoud Engelfriet,
	  \emph{The DES enc,yption algorithm}
	  http://www.itl.nist.gov/fipspubs/fip46-2.htm,
	  2003.
	\bibitem{public}
	  some guy,
	  \emph{public}
	  don't know yet,
	  2003.
	\bibitem{cracked}
	  Dave Rudolf,
	  \emph{Optimized Differential Cryptanalysis of the Data Encryption Standard}
	  University of Saskatchewan, http://davrud.sasktelwebsite.net/programming/des/,
	  2001.
\end{thebibliography}

\end{document}
